\chapter{Benchmark Specification}
\label{sec:benchmark-specification}

\section{Design Concepts}

\ldbcfinbench is intended to be a credible, fairand representative benchmark.
It's designed with the following concepts:

\begin{itemize}
      \item \textbf{Based on real systems}. The task force members gathering
            together from industry and academia intends to design \ldbcfinbench
            to express and emphasize the special patterns of data and workload
            distinguished from other popular benchmarks. In order to do that,
            \ldbcfinbench is designed based on the rich practical experience of
            member and additional surveys.
      \item \textbf{Comprehensive and complete.} \ldbcfinbench is intended to
            cover most demands encountered in the management of complexly
            structured data in financial scenarios.
      \item \textbf{Challenging and instructive.} Benchmarks are known to direct
            product development in certain directions. \ldbcfinbench is informed
            by the state-of-the-art in database research and industry practice
            to offer optimization challenges.
      \item \textbf{Easy to use and extendable.} As a benchmark offering value
            to many relevant stakeholders, \ldbcfinbench is designed to be easy
            for usage. The effort for obtaining test results with it should be
            small.
      \item \textbf{Modularized.} \ldbcfinbench is broken into parts both in
            design and benchmark suite that can be individually addressed to
            stimulate innovation without imposing an overly high threshold for
            participation.
      \item \textbf{Reproducible and documented.} \ldbcfinbench is intended to
            specify the auditing rules and provide full disclosure reports of
            auditing of benchmark runs in accordance with the LDBC
            Bylaws~\cite{ldbc_byelaws}.
\end{itemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Benchmark Workflow}
 [TODO: To be specified]

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
