\execSummary{
    Inspired by \ldbcsnb(LDBC's Social Network Benchmark), a task force is organized by AntGroup(Ant Group Co.,Ltd) and
    formed by the principal actors in the field of financial graph-like data management under the guidance and help from
    LDBC to design \ldbcfinbench(LDBC's Financial Benchmark) which is more applicable to financial scenarios. The task
    force is committed to define a framework that can fairly test and compare different graph based technologies where
    the dataset and workload are carefully designed with the rich practical experience of members in financial industry
    by hosting financial business itself or serving other financial entities. \ldbcfinbench is an industrial and academic
    initiative which is distinguished and characterized by the special features and patterns in financial industry.

    In this version, the task force has finished the design of the benchmark framework without the analytics workload which
    is future work. Meantime, the task force has also organized a developer group to develop the benchmark suite for \ldbcfinbench.
    The benchmark suite is currently under development according to the benchmark framework design. In the future, \ldbcfinbench
    will be improved continously with more feedback and more workloads including analytics workload will be designed and added.
    Please feel free to contract us if you have some suggestions or you are interested in joining in \ldbcfinbench.

    This document contains:
    \begin{itemize}
        \item A detailed specification of the data and workloads in the whole \ldbcfinbench.
        \item A detailed specification of the workflow and instructions about how to use the benchmark suite.
        \item A detailed specification of the auditing rules and the full disclosure report's required contents.
    \end{itemize}
}
