\chapter{Online Workload}
\label{section:online-workload}

This workload consists of a set of relatively simple read queries, write queries
and read-write operations, that touch a significant amount of data. These
queries and operations are usually considered as online data processing and
analysis in online financial systems. The LDBC FinBench Online workload consists
of three query classes: 
\begin{itemize}
    \item Read queries. See \autoref{sec:read-queries}. This section contains many basic read
    queries that are typical in financial scenarios.
    \item Write queries. See \autoref{sec:write-queries}. This section contains many basic
    write queries that are typical in financial scenarios.
    \item Read-write queries. See \autoref{sec:rw-queries}. This section contains many
    read-write operations composed of basic reads and writes in section 4.1 and
    4.2. In each operation, the basic reads and writes are supposed to launch
    step by step consecutively. The result may be wrong if the previous reads
    and writes are not be processed accurately in time. This feature of FinBench
    is a big difference from LDBC SNB.
\end{itemize}

\section{Read Queries}
\label{sec:read-queries}

\input{online-read-queries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Write Queries}
\label{sec:write-queries}

\input{online-write-queries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Read-Write Queries}
\label{sec:rw-queries}

\input{online-rw-queries}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
